The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2022-01-01 paper.tex
update

  \begin{enumerate}
    \item X-ray:
       \begin{enumerate}
         \item Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
               using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
               implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.
       \end{enumerate}
    \item Gamma-ray:
       \begin{enumerate}
         \item Leptonic process:\\
          The gamma-ray emission is produced by inverse Comptom scattering of the ISRF by CRe.
         \item Hadronic process:\\
          In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
          and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
          \begin{equation}
             \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
          \end{equation}
       \end{enumerate}
  \end{enumerate}

@@

\subsubsection{Leptonic process}

In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution with a spectral index 2 and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

@@

\subsubsection{Hadronic process}
\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} =\
   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}

>>>>

Thermal bremsstrahlung: The X-ray emissivity in an energy range 1.4–1.6 keV is calculated\
using the MEKAL model \citep{Xray-1,Xray-2,Xray-3}\
implemented in the utility XSPEC \citep{XSPEC}, assuming solar metallicity.\

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution with a spectral index 2 and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

@@

\subsubsection{Hadronic process}
In the hadronic model, CRp undergo hadronic collisions with thermal gas protons\
and produce $\gamma$-ray via pion decay. The volume emissivity of the emission can be written as
\begin{equation}
   \epsilon \propto U_{\text{CRp}}n_{p}\sigma_{p}\kappa_{pp}.
\end{equation}

\begin{equation}
  \frac{dE}{dtd\epsilon_{1}dV} =\
   cn_{H}pC\left(\frac{\epsilon_{1}}{m_{\text{p}}c^2}\right)^{-p}\
   \int_{0}^{1}\sigma(\epsilon_{\text{p}}) F(x,\epsilon_{\text{p}}) x^{p}dx.
\end{equation}
